Assessing primitives performance\\ on multi-stage execution

### 2018-05-07 paper.tex
add missing DOI
added figure * for bench
add gcc boxplots - all versions. the display will be improved

%%%%%
% END OLD
%%%%%

@@

taille 0

\begin{tikzpicture}
  \begin{axis}
  [
boxplot/draw direction
=y,
    xtick={1,2,3},
    xticklabels={Plugin, Slang, Slang+JIT},
    ]
    \addplot+[
    boxplot prepared={
      median=2.942,
      upper quartile=2.977,
      lower quartile=2.911,
      upper whisker=3.098,
      lower whisker=2.797
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.9594,
      upper quartile=0.9791,
      lower quartile=0.9230,
      upper whisker=1.1059,
      lower whisker=0.8705
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.4258,
      upper quartile=0.4310,
      lower quartile=0.4227,
      upper whisker=0.5181,
      lower whisker=0.4074
    },
    ] coordinates {};
  \end{axis}
\end{tikzpicture}

taille 5

\begin{tikzpicture}
  \begin{axis}
  [
boxplot/draw direction=y,
    xtick={1,2,3},
    xticklabels={Plugin, Slang, Slang+JIT},
    ]
    \addplot+[
    boxplot prepared={
      median=0.6904,
      upper quartile=0.6998,
      lower quartile=0.6835,
      upper whisker=0.7353,
      lower whisker=0.6407
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.2530,
      upper quartile=0.2594,
      lower quartile=0.2449,
      upper whisker=0.2836,
      lower whisker=0.2323
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.1455,
      upper quartile=0.1475,
      lower quartile=0.1425,
      upper whisker=0.1636,
      lower whisker=0.1266
    },
    ] coordinates {};
  \end{axis}
\end{tikzpicture}

taille 100
\begin{tikzpicture}
  \begin{axis}
  [
boxplot/draw direction=y,
    xtick={1,2,3},
    xticklabels={Plugin, Slang, Slang+JIT},
    ]
    \addplot+[
    boxplot prepared={
      median=0.10378,
      upper quartile=0.10435,
      lower quartile=0.10355,
      upper whisker=0.10586,
      lower whisker=0.09964
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.05689,
      upper quartile=0.05706,
      lower quartile=0.05648,
      upper whisker=0.05985,
      lower whisker=0.05527
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.05564,
      upper quartile=0.05560,
      lower quartile=0.05552,
      upper whisker=0.05985,
      lower whisker=0.05382
    },
    ] coordinates {};
  \end{axis}
\end{tikzpicture}

taille 10000
\begin{tikzpicture}
  \begin{axis}
  [
boxplot/draw direction
=y,
    xtick={1,2,3, 4},
    xticklabels={Baseline, Plugin, Slang, Slang+JIT},
    ]
    \addplot+[
    boxplot prepared={
      median=10474,
      upper quartile=10506,
      lower quartile=10455,
      upper whisker=11905,
      lower whisker=10099
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=761,
      upper quartile=761,
      lower quartile=761,
      upper whisker=765,
      lower whisker=760
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=476.7,
      upper quartile=477,
      lower quartile=476,
      upper whisker=482,
      lower whisker=475
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=500,
      upper quartile=501.8,
      lower quartile=500,
      upper whisker=512,
      lower whisker=499
    },
    ] coordinates {};
  \end{axis}
\end{tikzpicture}

@@

\section{Future work and conclusion}
1. number of representations\\
2. common representation
\cba{Future work -> primitive processor dependent (i.e. SSE4 instrs), pros and cons and why you did not do it (ingeniering cost per back-end)}
\cba{Inlining in Sista + ref}

>>>>

@@

\cba{Personnellement je ferais une figure, ou tu places tes graphes dedans, et pares tu referes a la figure dans le texte.}

\begin{figure*}
  \centering

    \begin{subfigure}[b]{.45\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
    boxplot/draw direction
    =y,
        xtick={1,2,3,4,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        font={\tiny}
        ]
        \addplot+[
        boxplot prepared={
          median=1,
          upper quartile=1,
          lower quartile=1,
          upper whisker=1,
          lower whisker=1
        },        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=0.3413,
          upper quartile=0.3421,
          lower quartile=0.3398,
          upper whisker=0.3559,
          lower whisker=0.3351
        },        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=0.3399,
          upper quartile=0.3409,
          lower quartile=0.3393,
          upper whisker=0.3569,
          lower whisker=0.3140
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=1.089,
          upper quartile=1.090,
          lower quartile=1.084,
          upper whisker=1.143,
          lower whisker=1.016
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=2.486,
          upper quartile=2.488,
          lower quartile=2.483,
          upper whisker=2.612,
          lower whisker=2.477
        },
        ] coordinates {};
      \end{axis}
    \end{tikzpicture}

    \subcaption{Taille 0}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
    boxplot/draw direction=y,
        xtick={1,2,3,4,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        font={\tiny}
        ]
        \addplot+[
        boxplot prepared={
          median=1,
          upper quartile=1,
          lower quartile=1,
          upper whisker=1,
          lower whisker=1
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=1.394,
          upper quartile=1.396,
          lower quartile=1.388,
          upper whisker=1.416,
          lower whisker=1.332
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=1.361,
          upper quartile=1.366,
          lower quartile=1.358,
          upper whisker=1.380,
          lower whisker=1.007
        },
        ] coordinates {};
                \addplot+[
        boxplot prepared={
          median=3.887,
          upper quartile=3.887,
          lower quartile=3.884,
          upper whisker=3.942,
          lower whisker=2.294
        },
        ] coordinates {};
                \addplot+[
        boxplot prepared={
          median=6.716,
          upper quartile=6.744,
          lower quartile=6.712,
          upper whisker=6.970,
          lower whisker=6.676
        },
        ] coordinates {};
      \end{axis}
    \end{tikzpicture}

    \subcaption{Taille 5}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
    boxplot/draw direction=y,
        xtick={1,2,3,4,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        font={\tiny}
        ]
        \addplot+[
        boxplot prepared={
          median=1,
          upper quartile=1,
          lower quartile=1,
          upper whisker=1,
          lower whisker=1
        },
        ] coordinates {};
         \addplot+[
        boxplot prepared={
          median=8.569,
          upper quartile=8.602,
          lower quartile=8.562,
          upper whisker=9.671,
          lower whisker=8.510
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=8.938,
          upper quartile=8.967,
          lower quartile=8.935,
          upper whisker=10.022,
          lower whisker=6.044
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=16.22,
          upper quartile=16.24,
          lower quartile=16.21,
          upper whisker=18.20,
          lower whisker=10.40
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=16.66,
          upper quartile=16.68,
          lower quartile=16.44,
          upper whisker=18.44,
          lower whisker=16.43
        },
        ] coordinates {};
      \end{axis}
    \end{tikzpicture}

    \subcaption{Taille 100}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
    boxplot/draw direction
    =y,
        xtick={1,2,3,4,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        font={\tiny}
        ]
        \addplot+[
        boxplot prepared={
          median=1,
          upper quartile=1,
          lower quartile=1,
          upper whisker=1,
          lower whisker=1
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=13.50,
          upper quartile=13.55,
          lower quartile=13.46,
          upper whisker=14.42,
          lower whisker=12.90
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=14.76,
          upper quartile=14.82,
          lower quartile=14.76,
          upper whisker=15.71,
          lower whisker=10.83
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=24.39,
          upper quartile=24.41,
          lower quartile=24.26,
          upper whisker=25.98,
          lower whisker=19.77
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=24.25,
          upper quartile=24.30,
          lower quartile=24.25,
          upper whisker=25.82,
          lower whisker=24.08
        },
        ] coordinates {};
      \end{axis}
    \end{tikzpicture}

   \subcaption{Taille 1000}
   \end{subfigure}
   \caption{GCC-Linux results}
\end{figure*}

@@

\section{Future work and conclusion}
1. number of representations\\
2. common representation
\cba{Future work -> primitive processor dependent (i.e. SSE4 instrs), pros and cons and why you did not do it (ingeniering cost per back-end)}
\cba{Inlining in Sista + ref}
\cite{SistaFastStartUp}
